```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message=FALSE}
library(openintro)
library(tidyverse)
library(janitor)

data(ncbirths)
```

## Usual Practice
1. If you are asked to install any packages install them by clicking the "Install" button in the yellow banner.
2. Always start by knitting any `.Rmd` file to make sure everything looks good. 
3. Always run R chunks provided to you before moving onto the rest of the document.
4. Write the [YAML part of](https://cosmos-uci-dshs.github.io/dshs-slides/week01/01b-intro-r.html#26) this document. 

---

Write out the examples from the slides.
```{r}
glimpse(ncbirths)
```
```{r}
count(ncbirths, premie)
```

```{r}
tabyl(ncbirths, premie)
```

```{r}
summarize(ncbirths, mean(weight))
```

```{r}
summarize(ncbirths, median(weight))
```

```{r}
summarize(ncbirths, quantile(weight, 0.75))
```

```{r}
summarize(ncbirths, var(weight))
```

```{r}
summarize(ncbirths, mean(weight), median(weight), sd(weight), var(weight))
```

```{r}
summarize(ncbirths, mean_weight = mean(weight), med_weight = median(weight),  sd_weight = sd(weight), var_weight = var(weight))
```

```{r}
summarize(ncbirths, mean(visits))
```

```{r}
summarize(ncbirths, mean(visits, na.rm = TRUE))
```




Do not copy-paste. 
Part of the learning process is making typos and trying to fix them.