```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message=FALSE}
library(openintro)
library(tidyverse)
babies <- babies %>% 
  mutate(smoke = as.logical(smoke),
         parity = as.logical(parity))

```

## Usual Practice
1. If you are asked to install any packages install them by clicking the "Install" button in the yellow banner.
2. Always start by knitting any `.Rmd` file to make sure everything looks good. 
3. Always run R chunks provided to you before moving onto the rest of the document.
4. Write the [YAML part of](https://cosmos-uci-dshs.github.io/dshs-slides/week01/01b-intro-r.html#26) this document. 

---

Write out the examples from the slides. 
Do not copy-paste. 

```{r}
ggplot(data = babies,
  aes(x=smoke)) +
geom_bar()
```

```{r}
ggplot(data = babies, 
       aes(x = bwt))+
  geom_histogram()
```
```{r}
ggplot(data = babies, 
       aes(x=bwt))+
  geom_histogram(binwidth = 15)
  
```
```{r}
ggplot(data = babies,
       aes(x = bwt)) +
  geom_histogram(binwidth = 15, 
                 color = "white",
                 fill = "deepskyblue")
```
```{r}
ggplot(data = babies, 
       aes(x = smoke,
           fill = parity)) + 
  geom_bar(position = "fill")
```

```{r}
ggplot(data = babies, 
       aes(x=smoke, 
           fill = parity))+
  geom_bar(position = "dodge")
```

```{r}
ggplot(babies, 
       aes(x = smoke, 
           y= bwt)) + 
  geom_boxplot()
```

```{r}
ggplot(babies, 
       aes(x = gestation, 
           y = bwt)) + 
  geom_point()
```
```{r}
ggplot(babies,
       aes(x = gestation,
           y = bwt,
           color = smoke)) +
  geom_point()
```
```{r}
ggplot(babies,
       aes(x = gestation,
           y = bwt,
           shape = smoke,
           color = smoke,
           size = weight)) +
  geom_point()
```


Part of the learning process is making typos and trying to fix them.