---
title: "04-Activity"
author: "Anish Thalamati"
date: "7/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


Racial Disparties in Maternal Mortality

1. What would a row of such data represent? 

A row of data would represent one pregnancy and mother and the data associated with it

2. What are the minimum required variables and the types of these variables that the researchers must have had in their dataset?

ID(integer), Race(char), Implicit Bias Training(Logical), mortality(logical), time of death(integer)  

Are there any other variables that you think that the researchers might have collected? If so, what would their types be?

Type of Job(Factor), Illness due to Birth(Logical), marital status(logical), social connections(logical), impartial bias test(logical), financial status(factor)

Heatwaves and Premature Child Birth 

1. What variables do you think the researchers must have collected?

Gestation period, survival of the infant, temperature, premature birth, time and date, infant status(ill,fine,dead)


2. What variables do you think the research might have collected?

Smoking, health issues, hospital, location 


```{r}
rheumdata <- readxl::read_excel("RheumArth_Tx_AgeComparisons.xlsx") %>%
  mutate(cdai_level = case_when(
    CDAI <=2.8 ~ "Remission", 
    CDAI > 2.8 & CDAI <= 10 ~ "Low Disease Activity",
    CDAI > 10 & CDAI <=22  ~ "Moderate Disease Activity",
    CDAI > 22 ~ "High Disease Activity")) %>%
  mutate(DAS_28_LVL = case_when(DAS_28 < 2.6~ "Remission",
                                 DAS_28 >= 2.6 & DAS_28 <=3.2 ~ "Low Disease Activity",
                                 DAS_28 > 3.2 & DAS_28 <= 5.1 ~ "Medium Disease Activity",
                                 DAS_28 > 5.1 ~ "High Disease Activity")) %>%
  mutate(sex = case_when(
    Sex == 0 ~ "Female",
    Sex == 1 ~ "Male")) %>%
  mutate(Steroids_GT_5 = case_when(
    Steroids_GT_5 == 0 ~ "No",
    Steroids_GT_5 == 1 ~ "Yes"
  )) %>%
  mutate(AgeGp = case_when(
    AgeGp == 1 ~ "Control",
    AgeGp == 2 ~ "Elderly"
  ))

```

```{r}
glimpse(rheumdata)
colnames(rheumdata)
```

Improved Questions 

1. Do “elderly” group have higher or lower CDAI overall when compared with the “control” group? Answer with a visual and numeric answers and comment on what you see.

2. Do women get diagnosed with AR at a later age than man? Answer with a visual and numbers. Comment on what you see.

New Questions 

1. How many patients are in remission?

2. Are there any patients who have been diagnosed with RA for longer than 40 years?

3. Are there any men who have been diagnosed with RA for longer than 40 years?
