```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message=FALSE}
library(openintro)
library(tidyverse)
babies <- babies %>% 
  mutate(smoke = as.logical(smoke),
         parity = as.logical(parity))

```

## Usual Practice
1. If you are asked to install any packages install them by clicking the "Install" button in the yellow banner.
2. Always start by knitting any `.Rmd` file to make sure everything looks good. 
3. Always run R chunks provided to you before moving onto the rest of the document.
4. Write the [YAML part of](https://cosmos-uci-dshs.github.io/dshs-slides/week01/01b-intro-r.html#26) this document. 

---

Write out the examples from the slides. 
Do not copy-paste. 
Part of the learning process is making typos and trying to fix them.

```{r}
ggplot(babies, 
       aes(x = gestation,
           y = bwt, 
           shape = smoke,
           color = smoke)) + 
  geom_point(size = 4) + 
  labs( x = "Gestastion (days)", 
        y = "Birth Weight (ounces)",
        title = "Gestation and Birth Weight by Mother's Smoker Status")+
  theme_bw()+
  theme(text = element_text(size = 10))+
  theme_classic() 
```

```{r}
ggplot(babies, 
       aes( x = gestation, 
            y = bwt,
            shape = smoke, 
            color = smoke)) + 
  geom_point(size = 4) + 
  facet_grid(.~parity)
```

```{r}
ggplot(babies, 
       aes( x = gestation, 
            y = bwt,
            shape = smoke, 
            color = smoke)) + 
  geom_point(size = 4) + 
  facet_grid(parity~.)
```

```{r}
c(4,8,16) %>%
  mean() %>%
  round()
```

