```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message=FALSE}
library(tidyverse)
library(fivethirtyeight)
library(openintro)
library(titanic)
data(candy_rankings)
data(titanic_train)
```


## Usual Practice
1. If you are asked to install any packages install them by clicking the "Install" button in the yellow banner.
2. Always start by knitting any `.Rmd` file to make sure everything looks good. 
3. Always run R chunks provided to you before moving onto the rest of the document.
4. Change the author of this document in the YAML part since it will consist of your work.

---

## Activity 1

1. Glimpse at the `candy_rankings` data frame.

```{r}
glimpse(candy_rankings)
```



2. Take a look at the head and tail of the `candy_rankings` data frame. 

```{r}
head(candy_rankings)
tail(candy_rankings)
```


3. How many variables are there in the `candy_rankings` data frame? Answer with inline code.

```{r}
ncol(candy_rankings)
```


There are `r ncol(candy_rankings)` variables in the dataframe 

4. How many observations are there in the `candy_rankings` data frame? Answer with inline code.

```{r}
nrow(candy_rankings)
```

There are `r nrow(candy_rankings)` observations in the dataframe 

Always knit your `.Rmd` file when you are done with an activity. 

---

## Activity 2

During this activity we will be working with the `titanic_train` data frame.

1. In the Console write `?titanic_train` to get to the documentation about this data frame. Familiarize yourself with the variables.  

2. Take a glimpse at the data.   

```{r}
glimpse(titanic_train)
```


3. Discuss in your groups if the variable types are correct.
If incorrect, note down what they should be changed to.

4. So far, we have used data from different sources and none of them were related to health sciences yet. 
We will change that pretty soon. In your groups, can you come up with logical, factor, integer, and double variables that could potentially be found in a hospital's database? 
If you keep coming up with more than one example for each, keep noting them down.

---

